---
title: "Water Level QA Check"
author: "OWRB"
date: "11/17/2021"
output: html_document
runtime: shiny
---

<!--
This script is designed to quickly QA large amounts of continuous data and flag sites/points that should be further investigated by the user. Points that the user deems outliers can be removed from the final dataset and shown in a separate csv file. 

This code was created by Zachary Tomlinson with the Oklahoma Water Resources Board (OWRB). Please direct any questions about the script to Zachary.Tomlinson@owrb.ok.gov
-->

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, comment = FALSE, message = FALSE )
```

This tool is used to QA large quantities of data by automatically flagging data that could have outliers and letting the user choose which potential outliers to remove from the final dataset. 

To start, select a statistic (or multiple statistics) for flagging potential outliers. These include data that lies in the outer 1% of the data distribution, data points that are more than 3 standard deviations from the mean, and data points that are fall outside the range of 1.5 * IQR. The default operator to combine statistics is ***And***, meaning that a given data point must meet all of selected statistics for it to be flagged. Switching to the ***Or*** operator flags any data point that meets any of the selected statistics. Therefore, ***Or*** flags more points than ***And***.

Once you have chosen your statistics to flag data, all of the flagged points will show up in the table on the left. A menu will also appear called ***Flagged Site Number***. This pulls up all of the data for a given site which contains some flagged measurements. Each site in the flagged site number menu will pull up a different graph with all of the data in that site. Flagged data points show up as orange, while non-flagged points show up as blue on the graph. You can zoom into the graph to get a better sense of the system and which points you may want to remove from the data. Also, you can opt to only see flagged points in the table for the current site by changing the default from *list flagged measurements for all sites* to *list flagged measurements for just the selected site*.

When you find a point you would like to remove from the data, click on its row in the table on the left. A table on the right will pop up, confirming you selected a point to remove. Lastly, hit ***Download*** to download the dataset minus the points that you selected to remove. 


```{r preprocess, echo = FALSE}
library(lubridate)
library(dplyr)
library(tidyverse)
library(dataRetrieval)
library(skimr)
library(data.table)
library(shinyWidgets)
library(lubridate)
library(DT)
library(plotly)

# Read in raw data, make sure formatting is correct
gwlev_raw = as.data.table(readRDS("gwlevels_raw.rds"))
gwlev_raw$site_no = as.character(gwlev_raw$site_no)
gwlev_raw$flagged = rep("No", nrow(gwlev_raw))  # Make a flagged data vector, all no initially
gwlev_raw$lev_dt = ymd(gwlev_raw$lev_dt)  # Convert date character to date object
gwlev_raw = unique(gwlev_raw)  # Remove duplicates

# Remove the QA'd removed data from the list
if(file.exists("QA_Removed.csv")){  # If QA removed data already exists, add it in
  outliers = read.csv("QA_Removed.csv")
  if(!file.exists("QA_removed_record.csv")){
    write.csv(outliers, "QA_removed_record.csv", row.names=FALSE)  # If a record of QA removed data doesn't exist, set it as the most recent
  }

  prev_outliers = read.csv("QA_removed_record.csv")  # Read in the record of QA removed data

  full_outliers = unique(rbind(prev_outliers,outliers))  # Combine record with current outliers

  # Reformat to match other formats
  full_outliers$site_no = as.character(full_outliers$site_no)
  full_outliers$lev_dt = ymd(full_outliers$lev_dt)
  full_outliers$gwl_ft_below_surf = as.numeric(full_outliers$gwl_ft_below_surf)

  full_outliers$Remove_now = rep("Yes", nrow(full_outliers))  # Make a vector saying we want to remove the data

  # Combine in the outliers with the data set, only the Remove_now vector remains
  gwlev_raw = left_join(gwlev_raw,full_outliers %>% select(site_no, lev_dt, gwl_ft_below_surf, Remove_now))
  
  # Remove NA values
  gwlev_raw = gwlev_raw[which(is.na(gwlev_raw$Remove_now)),]

  write.csv(full_outliers[,-ncol(full_outliers)], "QA_removed_record.csv", row.names = FALSE)
}

# Make a my_skim function to get the outside 1% range of data for each site_no
my_skim = skim_with(
      numeric = sfl(p0.5 = ~ quantile(., probs = 0.005), 
      p99.5 = ~quantile(., probs = 0.995)), append = TRUE)

# Perform the calculation on every site number
stats = gwlev_raw %>% group_by(site_no) %>%
    my_skim(gwl_ft_below_surf)

# Make an upper and lower limit for the IQR stat method
stats$upper_lim = stats$numeric.p75 +
  1.5*(stats$numeric.p75-stats$numeric.p25)
stats$lower_lim = stats$numeric.p25 -
  1.5*(stats$numeric.p75-stats$numeric.p25)

#Join stats to the raw data
gwlevel_join = left_join(gwlev_raw,stats)

# Obtain points outside the interquartile range
potential_outliers = which(gwlevel_join$gwl_ft_below_surf <
    gwlevel_join$lower_lim | gwlevel_join$gwl_ft_below_surf >
    gwlevel_join$upper_lim)

# Make a column indicating points outside the IQR limit
gwlevel_join$IQR_outliers = rep("No", nrow(gwlevel_join))
gwlevel_join$IQR_outliers[potential_outliers] = "Yes"

# Obtain points outside the 99% confidence interval
potential_outliers = which(gwlevel_join$gwl_ft_below_surf <
    gwlevel_join$numeric.p0.5|gwlevel_join$gwl_ft_below_surf >
    gwlevel_join$numeric.p99.5)

# Make a column indicating points outside the 99% limit
gwlevel_join$Perc_99_outliers = rep("No", nrow(gwlevel_join))
gwlevel_join$Perc_99_outliers[potential_outliers] = "Yes"

# Obtain points outside 3 standard deviations of the mean
gwlevel_join$z_scores = (gwlevel_join$gwl_ft_below_surf -
  mean(gwlevel_join$gwl_ft_below_surf))/sd(gwlevel_join$gwl_ft_below_surf)
potential_outliers = which(gwlevel_join$z_scores > 3 | gwlevel_join$z_scores < -3)

# Make a column indicating points outside the z-score limit
gwlevel_join$z_outliers = rep("No", nrow(gwlevel_join))
gwlevel_join$z_outliers[potential_outliers] = "Yes"

######## Make a vector of max change between 2 points and max site history change##################################
# Make a placeholder to put the column names in
all_changes = as.data.frame(matrix(nrow = 1, ncol = 3))
colnames(all_changes) = c("site_no","lev_dt", "meas_change")

# Make a site list
sites = unique(gwlevel_join$site_no)

# For each site, subtract each previous measurement from the current measurement and make it into a new data frame
for(site in sites){
  single_site = subset(gwlevel_join, site_no == site)  # Subset to only look at a single site
  single_site = single_site[order(single_site$lev_dt),]  # Order by date
  
  # Find the current measurement and previous measurement and subtract the previous measurement from the current
  # Add in date as well
  prev = single_site$gwl_ft_below_surf[-nrow(single_site)]
  current_meas = single_site$gwl_ft_below_surf[-1]
  change_stats = cbind.data.frame(single_site$site_no[-1], single_site$lev_dt[-1], current_meas - prev)
  
  # Make a data frame of measurement changes
  colnames(change_stats) = c("site_no","lev_dt", "meas_change")
  all_changes = bind_rows(all_changes, change_stats)
}

all_changes = all_changes[-1,]  # Remove the first row (an NA row left as a filler)

all_changes[which(is.na(gwlevel_join$meas_change)),"meas_change"] = 0  # Set all NA changes to 0

#Join to other statistics
gwlevel_join = left_join(gwlevel_join, all_changes)

# Make a user_remove vector for later
gwlevel_join$user_remove = rep("No", nrow(gwlevel_join))

gwlevel_join$site_no = as.character(gwlevel_join$site_no)  # Make sure formatting is correct
```


```{r}
ui = fluidPage(fluidRow(
  # Choose a statistic to flag info by
  column(6, multiInput( 
    inputId = "stat_choice", label = "Statistic for flagging potential outliers:", 
    choices =c("Outside 99th percentile", "Outside 3 standard deviations", "Outside 1.5xIQR", "Outside X ft from previous"))), 
  
  # Make site menu and input buttons, plus user download buttons
  column(6, uiOutput("inputsites"), 
    radioButtons("inclusivity", "Operator to combine statistics",choices = 
      c("And","Or")),downloadButton('downloadData','Download'),
    downloadButton('downloadRemoved', 
    HTML("Download and save <br/> removed data"))),
  
  # If Outside X ft of previous is chosen, pop up a conditional panel asking for the amount
  conditionalPanel(
      condition = 
        "input.stat_choice.indexOf('Outside X ft from previous') != -1",
      numericInput(inputId = "max_gap", label = "X = ", value = 1))),
  
  # Data table location and specifications
  fluidRow(column(8, DTOutput("table")), 
      column(4,radioButtons("tbl_view", "List flagged measurements for:",
      choices = c("all sites","just the selected site")),
      "Chosen outliers to remove:",tableOutput('table2'))),
  
  # Plot specifications (line or box plot)
  fluidRow(
    column(12, tabsetPanel(type = "tabs",
    tabPanel("Line Graph", plotlyOutput(outputId = "plot1")),
    tabPanel("Box Plot", plotlyOutput("plot2")))
 )
))

server <- function(input, output, session) {
  
  #Make a reactive data set based on user stat choices
  new_data = reactive({
    gwlev_processed = gwlevel_join
      
    # Select columns corresponding to flagged measurements from the original data set based on user stat choice
      if("Outside 99th percentile" %in% input$stat_choice){
        c1 = select(gwlev_processed,Perc_99_outliers)
      } else c1 = NULL
      if("Outside 1.5xIQR" %in% input$stat_choice){
        c2 = select(gwlev_processed, IQR_outliers)
      } else c2 = NULL
      if("Outside 3 standard deviations" %in% input$stat_choice){
        c3 = select(gwlev_processed, z_outliers)
      } else c3 = NULL
      if("Outside X ft from previous" %in% input$stat_choice){
        gwlev_processed$meas_change = as.numeric(gwlev_processed$meas_change)
        
        r_id_exceeds = which(gwlev_processed$meas_change > input$max_gap | gwlev_processed$meas_change < input$max_gap * -1)
        gwlev_processed$range_outliers = rep("No", nrow(gwlev_processed))
        gwlev_processed$range_outliers[r_id_exceeds] = "Yes"
        c4 = select(gwlev_processed, range_outliers)
      } else c4 = NULL
    
    flag_df = cbind(c1,c2,c3,c4) # Build a data frame of flagged/non-flagged rows 
    flag_df$r_id = seq(1:nrow(flag_df)) # Name the rows

    if(input$inclusivity == "And"){
      
      # Select rows where all of the columns have a value of "Yes"
      # Have to iterate for each possible column dimension
      if(ncol(flag_df) == 2){  
        flag_ind = flag_df[which(flag_df[,1] == "Yes"),]$r_id
      } else if(ncol(flag_df) == 3){  
        flag_ind = flag_df[which(flag_df[,1] == "Yes" & 
            flag_df[,2] == "Yes"),]$r_id
      }else if(ncol(flag_df) == 4){
        flag_ind = flag_df[which(flag_df[,1] == "Yes" & 
            flag_df[,2] == "Yes" & flag_df[,3] == "Yes"),]$r_id
      }else if(ncol(flag_df) == 5){
        flag_ind = flag_df[which(flag_df[,1] == "Yes" & 
            flag_df[,2] == "Yes" & flag_df[,3] == "Yes" & flag_df[,4]) == "Yes",]$r_id
        }
    }else if(input$inclusivity == "Or"){
      
      # Select rows where at least one of the columns has a value of "Yes"
      # Have to iterate for each possible column dimension
      if(ncol(flag_df) == 2){
        flag_ind = flag_df[which(flag_df[,1] == "Yes"),]$r_id
      } else if(ncol(flag_df) == 3){
        flag_ind = flag_df[which(flag_df[,1] == "Yes" | 
            flag_df[,2] == "Yes"),]$r_id
      }else if(ncol(flag_df) == 4){
        flag_ind = flag_df[which(flag_df[,1] == "Yes" | 
            flag_df[,2] == "Yes" | flag_df[,3] == "Yes"),]$r_id
      }else if(ncol(flag_df) == 5){
        flag_ind = flag_df[which(flag_df[,1] == "Yes" | 
            flag_df[,2] == "Yes" | flag_df[,3] == "Yes" | flag_df[,4]) == "Yes",]$r_id
        }
    } else flag_ind = NULL
    gwlev_processed$flagged[flag_ind] = "Yes"  # Changed the value of flagged for the applicable rows
    flag_sites = unique(subset(gwlev_processed, flagged == "Yes")$site_no)  # Only consider those rows
    data = subset(gwlev_processed, site_no %in% flag_sites)  # Subset the gwlev data
  })
  # Make a reactive user input called flagged site number based on the flagged sites from user options
  output$inputsites <- renderUI({
    selectInput(
      inputId = "sites",
      label = "Flagged Site Number",
      choices = unique(new_data()$site_no))
    })
  # Make another reactive dataset for plot data including flagged and non-flagged measurements for user-selected site
  plot_data = reactive({
    all_flagged = new_data()
    data = subset(all_flagged, site_no == input$sites)
  })
  # Make a chart data set for only including flagged measurements which can be selected/removed
  # Table can include selected site or all possible sites. 
  chart_data = reactive({
    a = new_data()
    if(input$tbl_view == "all sites"){
      a = subset(a, flagged == "Yes") %>% 
        select(site_no, lev_dt, gwl_ft_below_surf)
      data = a
    } else {
      a = subset(a, flagged == "Yes" & site_no == input$sites) %>%
        select(site_no, lev_dt, gwl_ft_below_surf)
      data = a
    }
  })
  # Make a user-download data set by removing the measurements chosen to be removed. 
  user_download = reactive({
      ids = input$table_rows_selected
      if(length(ids) > 0){
        remove_df = chart_data()[ids,]
        remove_df$remove = rep("Yes", nrow(remove_df))
        keep_df = left_join(gwlev_raw, remove_df)
        keep_df$remove[which(is.na(keep_df$remove))] = "No"
        row.names(keep_df) = NULL
        data = keep_df %>% filter(remove != "Yes") %>%
        select(-remove)
      } else data = gwlev_raw
  })
  # Make another reactive data set containing the removed measurements
  user_removed = reactive({
      ids = input$table_rows_selected
      remove_df = chart_data()[ids,]
      remove_df$remove = rep("Yes", nrow(remove_df))
      keep_df = left_join(gwlev_raw, remove_df)
      keep_df$remove[which(is.na(keep_df$remove))] = "No"
      row.names(keep_df) = NULL
      data = keep_df %>% filter(remove == "Yes") %>%
        select(-remove)
  })
  # Make plotly line graph with two layers: one for flagged data and one for unflagged. 
  output$plot1 = renderPlotly({
      plot_data = plot_data()
      flag_data = subset(plot_data, flagged == "Yes")
      ymin = min(plot_data$gwl_ft_below_surf)*0.9  # Invert the y axis by flipping the min and max
      ymax = max(plot_data$gwl_ft_below_surf)*1.1
      
      p = plot_ly(plot_data, x = ~lev_dt) %>%
        add_trace(y = ~gwl_ft_below_surf, 
          type = 'scatter', mode = 'lines+markers', 
          name = "non-flagged") %>% 
        add_trace(x = flag_data$lev_dt, type = 'scatter',
          y = flag_data$gwl_ft_below_surf,
          mode = 'markers', name = "flagged") %>%
      layout(yaxis = list(range = c(ymax,ymin)))
      p  # Output the plot
  })
  # Make plotly box plot with points shown beside it, flagged points as a different color
    output$plot2 = renderPlotly({
      plot_data = plot_data()
      ymin = min(plot_data$gwl_ft_below_surf)*0.9
      ymax = max(plot_data$gwl_ft_below_surf)*1.1
      
      # Generate a fake y axis for the point distribution shown by the boxplot
      plot_data$lev_x = rnorm(nrow(plot_data),2,0.5)
      
      # Generate the scatter point distribution
      p1 = plot_ly(plot_data, y = ~gwl_ft_below_surf, x = ~lev_x) %>% add_markers(color = ~flagged) %>%
        layout(yaxis = list(range = c(ymax,ymin))) %>% layout(xaxis = list(nticks = 0, title = "",
            showgrid = FALSE, visible = FALSE),  
            legend = list(title = list(text = '<b> Flagged </b>')))
      
      p2 = plot_ly(plot_data, y = ~gwl_ft_below_surf, type = "box", name = "boxplot") %>% 
        layout(yaxis = list(range = c(ymax,ymin)))
      p <- subplot(p1, p2, shareY = TRUE, widths = c(0.2, 0.8), margin = 0) # Output the plot
      
      p
  })
  # Render data table of flagged potential outliers
  output$table = renderDT({
    datatable(chart_data())
  })
  # Make data table of selected actual outliers
  output$table2 = renderTable({
    a = chart_data() %>% select(-lev_dt)
    a$site_no = as.character(a$site_no)
    colnames(a) = c("Site", "GW Depth")
    ids = input$table_rows_selected
    a[ids,]
  })
  output$downloadData <- downloadHandler( # Set the options for the downloaded data file. 
    filename = function() {
      paste(getwd(),"/gwlevels.rds")
    },
    content = function(file) {
      saveRDS(user_download(), file)
    }
  )
  output$downloadRemoved = downloadHandler(  # Set options for downloaded QA removed data
    filename = function() {
      paste0(getwd(),"/QA_Removed.csv")
    },
    content = function(file) {
      write.csv(user_removed(), file, row.names = FALSE)
    }
  )

}

shinyApp(ui = ui, server = server, options = list(height = 900, width = "100%"))  # Run shiny app
```





